Telemetry Module for Solar Vehicle

### 2021-06-17 documentation/FinalPaper/paper.tex

\begin{figure}[h]
    \centering
    \includegraphics[trim={0 2cm 0 0 },clip]{documentation/images/EnhancedShockburst.pdf}
    \caption{The Enhanced Shockburst$^\copyright$ packet structure.}
    \label{fig:shockburst}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{documentation/images/prime_tabel.png}
    \caption{Valid combinations of prime numbers, marked by OOOOOO}
    \label{fig:prime_tabel}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{documentation/images/SCU_CircuitDiagram.pdf}
    \caption{The circuit diagram for the SCU.}
    \label{fig:SCU_circuit}
\end{figure}
% threads 
\subsection{Support Vehicle}
% threads
\subsection{\todo{Graphical User Interface}}
% GUI

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{documentation/images/EnhancedShockburst.pdf}
    \caption{The Enhanced Shockburst$^\copyright$ packet structure.}
    \label{fig:shockburst}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{documentation/images/prime_tabel.png}
    \caption{Valid combinations of prime numbers, marked by O}
    \label{fig:prime_tabel}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{documentation/images/SCU_CircuitDiagram.pdf}
    \caption{The circuit diagram for the SCU.}
    \label{fig:SCU_circuit}
\end{figure}
% threads 
\subsection{Support Vehicle}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{documentation/images/SVU_CircuitDiagram.pdf}
    \caption{The circuit diagram for the SVU.}
    \label{fig:SCU_circuit}
\end{figure}
% threads
\subsection{\todo{Graphical User Interface}}
% GUI
